systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-08-29 paper/trunk/systemfit_other.tex
corrected / harmonized punctuation marks around equations (first small comment of reviewer B)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@686 591db2bd-e0a0-4d22-8c19-2192dbb7da31

Since the true residuals of the estimated equations are generally not known,
the true covariance matrix of the residuals cannot be determined.
Thus, this covariance matrix must be calculated from the
\emph{estimated} residuals. 
Generally, the estimated covariance matrix of the residuals
($\widehat{\Sigma} = \left[ \widehat{\sigma}_{ij} \right]$)
can be calculated from the residuals of a first-step OLS or 2SLS estimation.
The following formula is often applied:
\begin{equation}
   \widehat{\sigma}_{ij} = \frac{ \widehat{u}_i' \widehat{u}_j }{ T }
   \label{eq:rcov0}
\end{equation}
where $T$ is the number of observations in each equation.
However, in finite samples this estimator is biased,
because it is not corrected for degrees of freedom.
The usual single-equation procedure to correct for degrees of freedom
cannot always be applied, because the number of regressors in each equation
might differ.
Two alternative approaches to calculate the residual covariance
matrix are
\begin{equation}
   \widehat{\sigma}_{ij} = \frac{ \widehat{u}_i' \widehat{u}_j }
   { \sqrt{ \left( T - K_i \right) \cdot \left( T - K_j \right) } }
   \label{eq:rcov1}
\end{equation}
and
\begin{equation}
   \widehat{\sigma}_{ij} = \frac{ \widehat{u}_i' \widehat{u}_j }
   { T - \max \left( K_i , K_j \right) }
   \label{eq:rcov3}
\end{equation}
where $K_i$ and $K_j$ are the number of regressors in equation
$i$ and $j$, respectively.
However, these formulas yield unbiased estimators only if $K_i = K_j$
\citep[p.\ 469]{judge85}. 
% Greene (2003, p. 344) says that the second is unbiased if i = j or K_i = K_j,
% whereas the first is unbiased only if i = j. 
% However, if K_i = K_j the first and the second are equal.
% Why is the first biased if K_i = K_j ???????????

A further approach to obtain the estimated residual covariance
matrix is \citep[p.\ 309]{zellner62c}
\begin{eqnarray}
   \widehat{\sigma}_{ij} & = & 
   \frac{ \widehat{u}_i' \widehat{u}_j } 
   { T - K_i - K_j + tr \left[ X_i \left( X_i' X_i \right)^{-1}
   X_i' X_j \left( X_j' X_j \right)^{-1} X_j' \right] }
   \label{eq:rcov2} \\
   & = &
   \frac{ \widehat{u}_i' \widehat{u}_j } 
   { T - K_i - K_j + tr \left[ \left( X_i' X_i \right)^{-1}
   X_i' X_j \left( X_j' X_j \right)^{-1} X_j' X_i \right] }
\end{eqnarray} 
This yields an unbiased estimator for all elements of $\Sigma$,
but even if $\widehat{\Sigma}$ is an unbiased estimator of $\Sigma$, 
its inverse $\widehat{\Sigma}^{-1}$ is not an unbiased estimator 
of $\Sigma^{-1}$ \citep[p.\ 322]{theil71}.
Furthermore, the covariance matrix calculated by (\ref{eq:rcov2})
is not necessarily positive semidefinite \citep[p.\ 322]{theil71}. 
Hence, °it is doubtful whether [this formula] is really superior to 
[(\ref{eq:rcov0})]° \citep[p.\ 322]{theil71}.

@@

The goodness of fit of each single equation can be measured by the
traditional $R^2$ values:
\begin{equation}
   R_i^2 = 1 - \frac{ \widehat{u}_i' \widehat{u}_i }
   { ( y_i - \overline{y_i} )' ( y_i - \overline{y_i} ) }
\end{equation}
where $R_i^2$ is the $R^2$ value of the $i$th equation
and $\overline{y_i}$ is the mean value of $y_i$.

The goodness of fit of the whole system can be measured by the
McElroy's $R^2$ value \citep{mcelroy77}: 
% also: \citep[p.\ 345]{greene03}
\begin{equation}
   R_*^2 = 1 - \frac{ \widehat{u}' \widehat{ \Omega }^{-1} \widehat{u} }
   { y' \left( \widehat{ \Sigma }^{-1} \otimes
   \left( I - \frac{i i'}{T} \right) \right) y }
\end{equation}
where $T$ is the number of observations in each equation,
$I$ is an $T \times T$ identity matrix and 
$i$ is a column vector of $T$ ones.

@@

The $F$ statistic for systems of equations is
\begin{equation}
F = \frac{
   ( R \widehat{\beta} - q )'
   ( R ( X' ( \widehat{\Sigma} \otimes I )^{-1} X )^{-1} R' )^{-1}
   ( R \widehat{\beta} - q ) /
   j
}{
   \widehat{u}' ( \widehat{\Sigma} \otimes I )^{-1} \widehat{u} /
   ( M \cdot T - K )
}
\end{equation}
where $j$ is the number of restrictions,
$M$ is the number of equations,
$T$ is the number of observations per equation,
$K$ is the total number of estimated coefficients, and
$\widehat{\Sigma}$ is the estimated residual covariance matrix
used in the estimation.
Under the null hypothesis, $F$ has an $F$ distribution
with $j$ and $M \cdot T - K$ degrees of freedom
\citep[p.\ 314]{theil71}.

The Wald statistic for systems of equations is
\begin{equation}
W =
   ( R \widehat{\beta} - q )'
   ( R \widehat{Cov} [ \widehat{\beta} ] R' )^{-1}
   ( R \widehat{\beta} - q )
\end{equation}
Asymptotically, $W$ has a $\chi^2$
distribution with $j$ degrees of freedom
under the null hypothesis
\citep[p.\ 347]{greene03}.

The LR statistic for systems of equations is
\begin{equation}
LR = T \cdot \left(
   log \left| \widehat{ \Sigma }_r \right|
   - log \left| \widehat{ \Sigma }_u \right|
   \right)
\end{equation}
where $T$ is the number of observations per equation, and 
$\widehat{\Sigma}_r$ and $\widehat{\Sigma}_u$ are
the residual covariance matrices calculated by formula (\ref{eq:rcov0})
of the restricted and unrestricted estimation, respectively.
Asymptotically, $LR$ has a $\chi^2$
distribution with $j$ degrees of freedom
under the null hypothesis
\citep[p.\ 349]{greene03}.

@@

\citet{hausman78} developed a test for misspecification.
The null hypothesis of the test is that all exogenous variables are
uncorrelated with all disturbance terms.
Under this hypothesis both the 2SLS and the 3SLS estimator are consistent
but only the 3SLS estimator is (asymptotically) efficient.
Under the alternative hypothesis the 2SLS estimator is consistent
but the 3SLS estimator is inconsistent.
The Hausman test statistic is,
\begin{equation}
  m = \left( \widehat{\beta}_{2SLS} - \widehat{\beta}_{3SLS} \right)^{'}
      \left( \Cov \left[ \widehat{\beta}_{2SLS} \right] -
             \Cov \left[ \widehat{\beta}_{3SLS} \right] \right)
      \left( \widehat{\beta}_{2SLS} - \widehat{\beta}_{3SLS} \right)
\label{eq:hausman}
\end{equation}
where $\widehat{\beta}_{2SLS}$ and $\Cov \left[ \widehat{\beta}_{2SLS} \right]$ are the estimated
coefficient and covariance matrix from 2SLS estimation, and
$\widehat{\beta}_{3SLS}$ and $\Cov \left[ \widehat{\beta}_{3SLS} \right]$ are the estimated
coefficients and covariance matrix from 3SLS estimation.
Under the null hypothesis this test statistic has a
$\chi^2$ distribution with degrees of freedom equal to the number of
estimated parameters.

>>>>

Since the true residuals of the estimated equations are generally not known,
the true covariance matrix of the residuals cannot be determined.
Thus, this covariance matrix must be calculated from the
\emph{estimated} residuals. 
Generally, the estimated covariance matrix of the residuals
($\widehat{\Sigma} = \left[ \widehat{\sigma}_{ij} \right]$)
can be calculated from the residuals of a first-step OLS or 2SLS estimation.
In many cases, the formula
\begin{equation}
   \widehat{\sigma}_{ij} = \frac{ \widehat{u}_i' \widehat{u}_j }{ T }
   \label{eq:rcov0}
\end{equation}
is applied, where $T$ is the number of observations in each equation.
However, in finite samples this estimator is biased,
because it is not corrected for degrees of freedom.
The usual single-equation procedure to correct for degrees of freedom
cannot always be applied, because the number of regressors in each equation
might differ.
Two alternative approaches to calculate the residual covariance
matrix are
\begin{equation}
   \widehat{\sigma}_{ij} = \frac{ \widehat{u}_i' \widehat{u}_j }
   { \sqrt{ \left( T - K_i \right) \cdot \left( T - K_j \right) } }
   \label{eq:rcov1}
\end{equation}
and
\begin{equation}
   \widehat{\sigma}_{ij} = \frac{ \widehat{u}_i' \widehat{u}_j }
   { T - \max \left( K_i , K_j \right) } \; ,
   \label{eq:rcov3}
\end{equation}
where $K_i$ and $K_j$ are the number of regressors in equation
$i$ and $j$, respectively.
However, these formulas yield unbiased estimators only if $K_i = K_j$
\citep[p.\ 469]{judge85}. 
% Greene (2003, p. 344) says that the second is unbiased if i = j or K_i = K_j,
% whereas the first is unbiased only if i = j. 
% However, if K_i = K_j the first and the second are equal.
% Why is the first biased if K_i = K_j ???????????

A further approach to obtain the estimated residual covariance
matrix is
\begin{eqnarray}
   \widehat{\sigma}_{ij} & = & 
   \frac{ \widehat{u}_i' \widehat{u}_j } 
   { T - K_i - K_j + tr \left[ X_i \left( X_i' X_i \right)^{-1}
   X_i' X_j \left( X_j' X_j \right)^{-1} X_j' \right] }
   \label{eq:rcov2} \\
   & = &
   \frac{ \widehat{u}_i' \widehat{u}_j } 
   { T - K_i - K_j + tr \left[ \left( X_i' X_i \right)^{-1}
   X_i' X_j \left( X_j' X_j \right)^{-1} X_j' X_i \right] }
\end{eqnarray} 
\citep[p.\ 309]{zellner62c}.
This yields an unbiased estimator for all elements of $\Sigma$,
but even if $\widehat{\Sigma}$ is an unbiased estimator of $\Sigma$, 
its inverse $\widehat{\Sigma}^{-1}$ is not an unbiased estimator 
of $\Sigma^{-1}$ \citep[p.\ 322]{theil71}.
Furthermore, the covariance matrix calculated by (\ref{eq:rcov2})
is not necessarily positive semidefinite \citep[p.\ 322]{theil71}. 
Hence, °it is doubtful whether [this formula] is really superior to 
[(\ref{eq:rcov0})]° \citep[p.\ 322]{theil71}.

@@

The goodness of fit of each single equation can be measured by the
traditional $R^2$ values
\begin{equation}
   R_i^2 = 1 - \frac{ \widehat{u}_i' \widehat{u}_i }
   { ( y_i - \overline{y_i} )' ( y_i - \overline{y_i} ) } \; ,
\end{equation}
where $R_i^2$ is the $R^2$ value of the $i$th equation
and $\overline{y_i}$ is the mean value of $y_i$.

The goodness of fit of the whole system can be measured by the
McElroy's $R^2$ value 
% also: \citep[p.\ 345]{greene03}
\begin{equation}
   R_*^2 = 1 - \frac{ \widehat{u}' \widehat{ \Omega }^{-1} \widehat{u} }
   { y' \left( \widehat{ \Sigma }^{-1} \otimes
   \left( I - \frac{i i'}{T} \right) \right) y }
\end{equation}
\citep{mcelroy77},
where $T$ is the number of observations in each equation,
$I$ is an $T \times T$ identity matrix and 
$i$ is a column vector of $T$ ones.

@@

The $F$ statistic for systems of equations is
\begin{equation}
F = \frac{
   ( R \widehat{\beta} - q )'
   ( R ( X' ( \widehat{\Sigma} \otimes I )^{-1} X )^{-1} R' )^{-1}
   ( R \widehat{\beta} - q ) /
   j
}{
   \widehat{u}' ( \widehat{\Sigma} \otimes I )^{-1} \widehat{u} /
   ( M \cdot T - K )
} \; ,
\end{equation}
where $j$ is the number of restrictions,
$M$ is the number of equations,
$T$ is the number of observations per equation,
$K$ is the total number of estimated coefficients, and
$\widehat{\Sigma}$ is the estimated residual covariance matrix
used in the estimation.
Under the null hypothesis, $F$ has an $F$ distribution
with $j$ and $M \cdot T - K$ degrees of freedom
\citep[p.\ 314]{theil71}.

The Wald statistic for systems of equations is
\begin{equation}
W =
   ( R \widehat{\beta} - q )'
   ( R \widehat{Cov} [ \widehat{\beta} ] R' )^{-1}
   ( R \widehat{\beta} - q ) .
\end{equation}
Asymptotically, $W$ has a $\chi^2$
distribution with $j$ degrees of freedom
under the null hypothesis
\citep[p.\ 347]{greene03}.

The LR statistic for systems of equations is
\begin{equation}
LR = T \cdot \left(
   log \left| \widehat{ \Sigma }_r \right|
   - log \left| \widehat{ \Sigma }_u \right|
   \right) ,
\end{equation}
where $T$ is the number of observations per equation, and 
$\widehat{\Sigma}_r$ and $\widehat{\Sigma}_u$ are
the residual covariance matrices calculated by formula (\ref{eq:rcov0})
of the restricted and unrestricted estimation, respectively.
Asymptotically, $LR$ has a $\chi^2$
distribution with $j$ degrees of freedom
under the null hypothesis
\citep[p.\ 349]{greene03}.

@@

\citet{hausman78} developed a test for misspecification.
The null hypothesis of the test is that all exogenous variables are
uncorrelated with all disturbance terms.
Under this hypothesis both the 2SLS and the 3SLS estimator are consistent
but only the 3SLS estimator is (asymptotically) efficient.
Under the alternative hypothesis the 2SLS estimator is consistent
but the 3SLS estimator is inconsistent.
The Hausman test statistic is
\begin{equation}
  m = \left( \widehat{\beta}_{2SLS} - \widehat{\beta}_{3SLS} \right)^{'}
      \left( \Cov \left[ \widehat{\beta}_{2SLS} \right] -
             \Cov \left[ \widehat{\beta}_{3SLS} \right] \right)
      \left( \widehat{\beta}_{2SLS} - \widehat{\beta}_{3SLS} \right) ,
\label{eq:hausman}
\end{equation}
where $\widehat{\beta}_{2SLS}$ and $\Cov \left[ \widehat{\beta}_{2SLS} \right]$ are the estimated
coefficient and covariance matrix from 2SLS estimation, and
$\widehat{\beta}_{3SLS}$ and $\Cov \left[ \widehat{\beta}_{3SLS} \right]$ are the estimated
coefficients and covariance matrix from 3SLS estimation.
Under the null hypothesis this test statistic has a
$\chi^2$ distribution with degrees of freedom equal to the number of
estimated parameters.

### 2006-08-29 paper/trunk/systemfit_restrictions.tex
corrected / harmonized punctuation marks around equations (first small comment of reviewer B)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@686 591db2bd-e0a0-4d22-8c19-2192dbb7da31

It is common to perform hypothesis tests by imposing restrictions on
the parameter estimates.
There are two ways to impose linear parameter restrictions.
First, a matrix $T$ can be specified that
\begin{equation}
   \beta = T \cdot \beta^* \label{eq:T-restr} 
\end{equation}
where $\beta^*$ is a vector of restricted (linear independent) coefficients,
and $T$ is a matrix with the number of rows equal to the number of
unrestricted coefficients ($\beta$) and
the number of columns equal to the number of restricted coefficients
($\beta^*$).
$T$ can be used to map each unrestricted coefficient to one or more
restricted coefficients.

To impose these restrictions, the $X$ matrix is
(post-)\hspace{0pt}multiplied by this $T$ matrix.
\begin{equation}
    X^* = X \cdot T
\end{equation}
Then, $X^*$ is substituted for $X$ and a standard estimation as described
in the previous section is done
(equations~\ref{eq:ols}--\ref{eq:3slsEViews}).
This results in the linear independent parameter estimates $\widehat{\beta}^*$ and
their covariance matrix.
The original parameters can be obtained by equation (\ref{eq:T-restr})
and the covariance matrix of the original parameters
can be obtained by:
\begin{equation}
   \Cov \left[ \widehat{\beta} \right] = T \cdot \Cov \left[ \widehat{\beta}^* \right] \cdot T'
\end{equation}

The second way to impose linear parameter restrictions
can be formulated by
\begin{equation}
   R \beta^0 = q
\end{equation}
where $\beta^0$ is the vector of the restricted coefficients, 
and $R$ and $q$ are a matrix and vector, respectively,
to impose the restrictions \citep[see][p.\ 100]{greene03}.
Each linear independent restriction is represented by one row of $R$
and the corresponding element of~$q$.

@@

These two methods can be combined.
In this case the restrictions imposed using the latter method are
imposed on the linear independent parameters due to the restrictions
imposed using the first method:
\begin{equation}
   R \beta^{*0} = q
\end{equation}
where $\beta^{*0}$ is the vector of the restricted $\beta^*$ coefficients.

@@

The OLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{OLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X' X & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X' y \\ q 
   \end{array} \right]
\end{equation}
where $\lambda$ is a vector of the Lagrangean multipliers of the restrictions.
If the whole system is treated as one single equation,
the covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{OLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = \sigma^2 
   \left[ \begin{array}{cc}
      X' X & R' \\ 
      R & 0
   \end{array} \right]^{-1}
\end{equation}
with $\sigma^2 = E \left( u' u \right)$.
If the disturbance terms of the individual equations
are allowed to have different variances, 
the covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{OLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1}
\end{equation}
with $\Omega = \Sigma \otimes I$, 
$\sigma_{ij} = 0 \; \forall \; i \neq j$ and
$\sigma_{ii} = E \left( u_i' u_i \right)$.

@@

The WLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{WLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X' \Omega^{-1} y \\ q 
   \end{array} \right]
\end{equation}
with $\Omega = \Sigma \otimes I$, 
$\sigma_{ij} = 0 \; \forall \; i \neq j$ and
$\sigma_{ii} = E \left( u_i' u_i \right)$.
The covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{WLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1}
\end{equation}

@@

The SUR estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{SUR} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X' \Omega^{-1} y \\ q 
   \end{array} \right]
\end{equation}
with $\Omega = \Sigma \otimes I$ and
$\sigma_{ij} = E \left( u_i' u_j \right)$.
The covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{SUR} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1}
\end{equation}

@@

The 2SLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{2SLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \widehat{X}' \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \widehat{X}' y \\ q 
   \end{array} \right]
   \label{eq:beta2SLSr}
\end{equation}
If the whole system is treated as one single equation,
the covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{2SLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = \sigma^2 
   \left[ \begin{array}{cc}
      \widehat{X}' \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1}
\end{equation}
with $\sigma^2 = E \left( u' u \right)$.
If the disturbance terms of the individual equations
are allowed to have different variances, 
the covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{2SLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      \widehat{X}' \Omega^{-1} \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1}
\end{equation}
with $\Omega = \Sigma \otimes I$, 
$\sigma_{ij} = 0 \; \forall \; i \neq j$ and
$\sigma_{ii} = E \left( u_i' u_i \right)$.

@@

The W2SLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{W2SLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \widehat{X}' \Omega^{-1} \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \widehat{X}' \Omega^{-1} y \\ q 
   \end{array} \right]
\end{equation}
with $\Omega = \Sigma \otimes I$, 
$\sigma_{ij} = 0 \; \forall \; i \neq j$ and
$\sigma_{ii} = E \left( u_i' u_i \right)$.
The covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{W2SLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      \widehat{X}' \Omega^{-1} \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1}
\end{equation}

@@

@@

with $\Omega = \Sigma \otimes I$ and

@@

@@

with

@@

\cite{schmidt90} is:

@@

The econometrics software EViews calculates the restricted 3SLS estimator by:

>>>>

It is common to perform hypothesis tests by imposing restrictions on
the parameter estimates.
There are two ways to impose linear parameter restrictions.
First, a matrix $T$ can be specified that
\begin{equation}
   \beta = T \cdot \beta^* \label{eq:T-restr} ,
\end{equation}
where $\beta^*$ is a vector of restricted (linear independent) coefficients,
and $T$ is a matrix with the number of rows equal to the number of
unrestricted coefficients ($\beta$) and
the number of columns equal to the number of restricted coefficients
($\beta^*$).
$T$ can be used to map each unrestricted coefficient to one or more
restricted coefficients.

To impose these restrictions, the $X$ matrix is
(post-)\hspace{0pt}multiplied by this $T$ matrix, so that
\begin{equation}
    X^* = X \cdot T .
\end{equation}
Then, $X^*$ is substituted for $X$ and a standard estimation as described
in the previous section is done
(equations~\ref{eq:ols}--\ref{eq:3slsEViews}).
This results in the linear independent parameter estimates $\widehat{\beta}^*$ and
their covariance matrix.
The original parameters can be obtained by equation (\ref{eq:T-restr})
and the covariance matrix of the original parameters
can be obtained by
\begin{equation}
   \Cov \left[ \widehat{\beta} \right]
   = T \cdot \Cov \left[ \widehat{\beta}^* \right] \cdot T' .
\end{equation}

The second way to impose linear parameter restrictions
can be formulated by
\begin{equation}
   R \beta^0 = q ,
\end{equation}
where $\beta^0$ is the vector of the restricted coefficients, 
and $R$ and $q$ are a matrix and vector, respectively,
to impose the restrictions \citep[see][p.\ 100]{greene03}.
Each linear independent restriction is represented by one row of $R$
and the corresponding element of~$q$.

@@

These two methods can be combined.
In this case the restrictions imposed using the latter method are
imposed on the linear independent parameters due to the restrictions
imposed using the first method, so that
\begin{equation}
   R \beta^{*0} = q ,
\end{equation}
where $\beta^{*0}$ is the vector of the restricted $\beta^*$ coefficients.

@@

The OLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{OLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X' X & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X' y \\ q 
   \end{array} \right] ,
\end{equation}
where $\lambda$ is a vector of the Lagrangean multipliers of the restrictions.
If the whole system is treated as one single equation,
the covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{OLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = \sigma^2 
   \left[ \begin{array}{cc}
      X' X & R' \\ 
      R & 0
   \end{array} \right]^{-1} ,
\end{equation}
where $\sigma^2 = E \left( u' u \right)$.
If the disturbance terms of the individual equations
are allowed to have different variances, 
the covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{OLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1} ,
\end{equation}
where $\Omega = \Sigma \otimes I$,
$\sigma_{ij} = 0 \; \forall \; i \neq j$ and
$\sigma_{ii} = E \left( u_i' u_i \right)$.

@@

The WLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{WLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X' \Omega^{-1} y \\ q 
   \end{array} \right] ,
\end{equation}
where $\Omega = \Sigma \otimes I$,
$\sigma_{ij} = 0 \; \forall \; i \neq j$ and
$\sigma_{ii} = E \left( u_i' u_i \right)$.
The covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{WLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1} .
\end{equation}

@@

The SUR estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{SUR} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X' \Omega^{-1} y \\ q 
   \end{array} \right] ,
\end{equation}
where $\Omega = \Sigma \otimes I$ and
$\sigma_{ij} = E \left( u_i' u_j \right)$.
The covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{SUR} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1} .
\end{equation}

@@

The 2SLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{2SLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \widehat{X}' \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \widehat{X}' y \\ q 
   \end{array} \right] .
   \label{eq:beta2SLSr}
\end{equation}
If the whole system is treated as one single equation,
the covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{2SLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = \sigma^2 
   \left[ \begin{array}{cc}
      \widehat{X}' \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1} ,
\end{equation}
where $\sigma^2 = E \left( u' u \right)$.
If the disturbance terms of the individual equations
are allowed to have different variances, 
the covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{2SLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      \widehat{X}' \Omega^{-1} \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1} ,
\end{equation}
where $\Omega = \Sigma \otimes I$,
$\sigma_{ij} = 0 \; \forall \; i \neq j$ and
$\sigma_{ii} = E \left( u_i' u_i \right)$.

@@

The W2SLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{W2SLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \widehat{X}' \Omega^{-1} \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \widehat{X}' \Omega^{-1} y \\ q 
   \end{array} \right] ,
\end{equation}
where $\Omega = \Sigma \otimes I$,
$\sigma_{ij} = 0 \; \forall \; i \neq j$ and
$\sigma_{ii} = E \left( u_i' u_i \right)$.
The covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{W2SLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      \widehat{X}' \Omega^{-1} \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1} .
\end{equation}

@@

   \end{array} \right] ,

@@

where $\Omega = \Sigma \otimes I$ and

@@

   \end{array} \right]^{-1} .

@@

where

@@

\cite{schmidt90} is

@@

The econometrics software EViews calculates the restricted 3SLS estimator by

### 2006-08-29 paper/trunk/systemfit_statistics.tex
gotta get my changes in...
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@645 591db2bd-e0a0-4d22-8c19-2192dbb7da31
corrected / harmonized punctuation marks around equations (first small comment of reviewer B)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@686 591db2bd-e0a0-4d22-8c19-2192dbb7da31

Consider a system of $G$ equations, where the $i$th equation is of
the form 
\begin{equation}
   y_{i} = X_i \beta_i + u_i, \quad i = 1, 2, \ldots, G
\end{equation}
where $y_i$ is a vector of the dependent variable,
$X_i$ is a matrix of the exogenous variables,
$\beta_i$ is the coefficient vector and
$u_i$ is a vector of the disturbance terms of the $i$th equation.

@@

or more simply as
\begin{equation}
   y = X \beta + u 
\end{equation}

We assume that there is no correlation of the disturbance terms 
across observations:
\begin{equation}
   E \left( u_{it} \, u_{jt^*} \right) = 0 
   \; \forall \; t \neq t^*
\end{equation}
where $i$ and $j$ indicate the equation number 
and $t$ and $t^*$ denote the observation number.

However, we explicitly allow for contemporaneous correlation:
\begin{equation}
   E \left( u_{it} \, u_{jt} \right) = \sigma_{ij}
\end{equation}

Thus, the covariance matrix of the total system is
\begin{equation}
   E \left( u \, u' \right) = \Omega = \Sigma \otimes I
\end{equation}
where $\Sigma = \left[ \sigma_{ij} \right]$ is the residual covariance matrix
and $I$ is an identity matrix.

>>>>

Consider a system of $G$ equations, where the $i$th equation is of
the form 
\begin{equation}
   y_{i} = X_i \beta_i + u_i, \quad i = 1, 2, \ldots, G ,
\end{equation}
where $y_i$ is a vector of the dependent variable,
$X_i$ is a matrix of the exogenous variables,
$\beta_i$ is the coefficient vector and
$u_i$ is a vector of the disturbance terms of the $i$th equation.

@@

or more simply as
\begin{equation}
   y = X \beta + u .
\end{equation}

We assume that there is no correlation of the disturbance terms 
across observations, so that
\begin{equation}
   E \left( u_{it} \, u_{jt^*} \right) = 0 
   \; \forall \; t \neq t^* ,
\end{equation}
where $i$ and $j$ indicate the equation number 
and $t$ and $t^*$ denote the observation number.

However, we explicitly allow for contemporaneous correlation, i.e.\
\begin{equation}
   E \left( u_{it} \, u_{jt} \right) = \sigma_{ij} .
\end{equation}

Thus, the covariance matrix of the total system is
\begin{equation}
   E \left( u \, u' \right) = \Omega = \Sigma \otimes I ,
\end{equation}
where $\Sigma = \left[ \sigma_{ij} \right]$ is the residual covariance matrix
and $I$ is an identity matrix.
